---
title: "Kotoboo_data_viz"
author: "ASM"
date: "04/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
library(janitor)
library(readxl)
library(stringr)
library(lme4)
library(lmerTest)
library(ggplot2)
#library(tidylog)

#function for finding mode
find_mode <- function(x) {
     u <- unique(x)
     tab <- tabulate(match(x, u))
     u[tab == max(tab)]
}
```


# read in data
```{r}
x_2022_september_qualtrics_data <- read_excel("2022_september_qualtrics_data.xlsx", col_names=c("start_date", "end_date", "response_type", "progress", "duration_s", "finished", "recorded_date", "response_id","distribution_channel", "user_language", "recaptcha_score","consent", "year_birth", "gender","country", "not_caregiver", "is_parent","is_teacher","is_grandparent", "is_babysitter","is_aunt_uncle","is_sibling","is_therapist", "is_neighbour","is_family_friend", "is_other","visit_kotoboo", "how_helpful_evidence_based", "how_often_internet","which_topics_bilingualism","which_topics_screen_time","which_topics_lang_diversity","which_topics_sign_langauge","which_topics_foster_language","which_topics_reading_writing","which_topics_langauge_dev_disorders","which_topics_mythbusters","importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other","importance_other_text", "participate_in_science", "comic_ideas", "comic_ideas_text", "sc0_score", "language", "q_language"))

x_2022_september_qualtrics_data <- x_2022_september_qualtrics_data [-c(1,2,3,4),]

```


# exclude data
```{r}
# total number of response
nrow(x_2022_september_qualtrics_data) # n = 203 (n of pre-exclusion)


# identify those who did not satisfy the completion rate (i.e., no response from Q5 onwards)
## first, check completion per question
x_2022_september_qualtrics_data <- x_2022_september_qualtrics_data %>%
  # check if there's any response (flag NA = 0)
  mutate(completed_Q1 = ifelse(is.na(year_birth), 0, 1),
         completed_Q2 = ifelse(is.na(gender), 0, 1),
         completed_Q3 = ifelse(is.na(country), 0, 1),
         completed_Q4 = case_when(if_all(c(starts_with("is_"), not_caregiver), is.na) ~ 0,
                             TRUE ~ 1),
         flag_Q5 = ifelse(is.na(visit_kotoboo), 0, 1),
         flag_Q6 = ifelse(is.na(how_helpful_evidence_based), 0, 1),
         flag_Q7 = ifelse(is.na(how_often_internet), 0, 1),
         flag_Q8 = case_when(if_all(starts_with("which_topics"), is.na) ~ 0,
                             TRUE ~ 1),
         flag_Q9 = case_when(if_all(starts_with("importance_"), is.na) ~ 0,
                             TRUE ~ 1),
         flag_Q10 = ifelse(is.na(participate_in_science), 0, 1),
         flag_Q11 = ifelse(is.na(comic_ideas), 0, 1)) %>%
  # create a new variable indicating no response from Q5 onward
  mutate(no_response = case_when(if_all(starts_with("flag_"), ~ . == 0) ~ 1,
                                 TRUE ~ 0)) 

## identify response_id with no responses from Q5 onward 
exclusion_completion <- x_2022_september_qualtrics_data %>%
  filter(no_response == 1) %>%
  distinct(response_id)


# now run all the exclusion criteria
## 203 (n of pre-exclusion)
x_2022_september_qualtrics_data <- x_2022_september_qualtrics_data %>%
  filter(recaptcha_score >=.80) %>% #200 3 excluded
  filter(year_birth <=2004) %>% #161 39 excluded
  filter(year_birth >=1922) %>% #161 0 excluded
  filter(consent=="I consent") %>% #161 0 excluded
  anti_join(exclusion_completion) %>% #149 12 excluded
  filter(is_parent=="Parent") #126 23 excluded

```


# get demographic info
## 1. gender
```{r}
sum(x_2022_september_qualtrics_data$gender=="Female", na.rm = T) #100 female
sum(x_2022_september_qualtrics_data$gender=="Male", na.rm = T)  # 23 male
sum(x_2022_september_qualtrics_data$gender=="Prefer not to answer", na.rm = T) #3

```

## 2. by country info
```{r}
country_table <- x_2022_september_qualtrics_data %>%
  select(response_id, country) %>%
  group_by(country) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(total_n = sum(n),
         n_percent = round(n/total_n * 100, 1)) %>%
  arrange(desc(n_percent))

country_table
#I will make a png map with this info
```


## 3. age range
```{r}
#Age range
x_2022_september_qualtrics_data <- x_2022_september_qualtrics_data %>%
  mutate(survey_year = 2022) %>%
  mutate(age = survey_year - as.numeric(year_birth))

range(x_2022_september_qualtrics_data$age) #19-63 years
mean(x_2022_september_qualtrics_data$age) #36.08 years
sd(x_2022_september_qualtrics_data$age) #5.92
``` 

## 4. average time spent in survey (take median as the better measure)
```{r}
mean(as.numeric(x_2022_september_qualtrics_data$duration_s)) # 15522.56
median(as.numeric(x_2022_september_qualtrics_data$duration_s))#237
#table(x_2022_september_qualtrics_data$duration_s)

# to minutes
median(as.numeric(x_2022_september_qualtrics_data$duration_s))/60 #3.95
```

## 5. completion rate stats
```{r}
# calculate completion rate per participant
x_2022_september_qualtrics_data <- x_2022_september_qualtrics_data %>%
  mutate(sum_q_completed = rowSums(across(starts_with(c("completed_", "flag_"))), na.rm = TRUE),
         rate_completed = round(sum_q_completed / 11 * 100, 2)) %>%
  select(-starts_with(c("completed_", "flag_"))) #remove unnecessary variables

# mean, range, sd of completion rate
round(mean(as.numeric(x_2022_september_qualtrics_data$rate_completed)), 2) # mean of 94.58% completion
round(range(as.numeric(x_2022_september_qualtrics_data$rate_completed))) #45-100% completed
round(sd(as.numeric(x_2022_september_qualtrics_data$rate_completed)), 2) # sd of 12.76%

```
## 6. kotoboo visit (Q5 on questionnaire)
```{r}
visits <- x_2022_september_qualtrics_data %>%
  select(visit_kotoboo)

visits_table<- as.data.frame(table(visits$visit_kotoboo)) 

visits_table<- visits_table %>%
  mutate(percentage = round(Freq/nrow(x_2022_september_qualtrics_data)*100)) %>%
  arrange(desc(percentage))

visits_table
```

## caregivers' breakdown---- not relevant any more as we decided to only keep parents. 
```{r}
#caregivers <- x_2022_september_qualtrics_data %>%
 # select(not_caregiver, starts_with("is_")) %>%
  #mutate_all(funs(replace(., !is.na(.), 1))) %>%
  #mutate_all(funs(as.numeric))

#caregivers_sums <- caregivers %>%
 # summarise_all(.funs = c(sum = "sum"), na.rm = T) %>%
  #pivot_longer(everything(), names_to = "caregiver_type", values_to = "sum") %>%
  #mutate(percentage = round(sum / nrow(x_2022_september_qualtrics_data) * 100)) %>%
  #arrange(desc(percentage))

#A. Percentage of caregivers
#careg<- x_2022_september_qualtrics_data %>%
 # select(c(not_caregiver, is_parent, is_teacher, is_grandparent, is_babysitter, is_aunt_uncle,
  #         is_sibling, is_therapist, is_neighbour, is_family_friend, is_other))  %>%
  #mutate(not_caregiver = case_when(not_caregiver == "I am not a caregiver" ~ "T",
   #                                TRUE~"F")) %>%
    #mutate(is_parent = case_when(is_parent == "Parent" ~ "T",
     #                              TRUE~"F")) %>%
    #mutate(is_teacher = case_when(is_teacher == "Teacher/Educator" ~ "T",
     #                              TRUE~"F")) %>%
      #mutate(is_grandparent = case_when(is_grandparent == "Grandparent" ~ "T",
       #                            TRUE~"F")) %>%
        #mutate(is_babysitter = case_when(is_babysitter == "Nanny/Babysitter" ~ "T",
         #                          TRUE~"F")) %>%
        #mutate(is_aunt_uncle = case_when(is_aunt_uncle == "Uncle/Aunt" ~ "T",
         #                          TRUE~"F"))%>%
        #mutate(is_sibling = case_when(is_sibling == "Sibling" ~ "T",
         #                          TRUE~"F")) %>%
        #mutate(is_therapist = case_when(is_therapist == "Therapist" ~ "T",
         #                          TRUE~"F")) %>%
        #mutate(is_neighbour = case_when(is_neighbour == "Neighbour" ~ "T",
         #                          TRUE~"F")) %>%
        #mutate(is_family_friend = case_when(is_family_friend == "Family friend" ~ "T",
         #                          TRUE~"F")) %>%
          #mutate(is_other = case_when(is_other == "Other" ~ "T",
           #                        TRUE~"F")) %>%
  #count(not_caregiver, is_parent, is_teacher, is_grandparent, is_babysitter, is_aunt_uncle,
   #        is_sibling, is_therapist, is_neighbour, is_family_friend, is_other, sort=T)

#only_parents <- careg %>%
 # select(is_parent, n) %>%
#  filter (is_parent == "T") 

#sum(only_parents$n)
```


# Main analysis
## Internet search mode and mean (Q7 on questionnaire)
```{r}
count_internet <- x_2022_september_qualtrics_data %>%
  filter(!is.na(how_often_internet)) %>%
  group_by(how_often_internet) %>%
  count(how_often_internet) %>%
  ungroup() %>%
  mutate(n_total = sum(n),
         percentage = (n/n_total)*100) %>%
  arrange(desc(percentage))

count_internet

# mode
find_mode(x_2022_september_qualtrics_data$how_often_internet)

# mean
internet_freq <- x_2022_september_qualtrics_data %>%
  mutate(internet_freq_numeric = case_when(
    str_detect(how_often_internet, "Never") ~ 1,
    str_detect(how_often_internet, "Rarely") ~ 2,
    str_detect(how_often_internet, "Occasionally") ~ 3,
    str_detect(how_often_internet, "Often") ~ 4,
    str_detect(how_often_internet, "Frequently") ~ 5,
    TRUE ~ NA_real_))

mean(internet_freq$internet_freq_numeric, na.rm=T)

# plot (n = 143)
plot_internet_freq <- count_internet %>%
  ## remove NAs
  #filter(!is.na(how_often_internet)) %>%
  # rename items
  mutate(how_often_internet = case_when(
    str_detect(how_often_internet, "Never") ~ "Never",
    str_detect(how_often_internet, "Rarely") ~ "Rarely (a few times a year)",
    str_detect(how_often_internet, "Occasionally") ~ "Occasionally (once a month)",
    str_detect(how_often_internet, "Often") ~ "Often (every other week)",
    str_detect(how_often_internet, "Frequently") ~ "Frequently (more than one a week)")) %>%
  ggplot() + 
  geom_bar(aes(x = factor(0), y = percentage, 
               fill = factor(how_often_internet, 
                             levels = c("Frequently (more than one a week)", "Often (every other week)", "Occasionally (once a month)", "Rarely (a few times a year)", "Never"))), 
               position="stack", stat="identity") +
  ylab("Percentage") +
  coord_flip() + 
  scale_fill_manual(values = c("#e31a1c", "#fb9a99", "#d9d9d9", "#6baed6", "#3182bd")) +
  theme_minimal(base_size = 20) +
  theme(legend.position="bottom",
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(title="Frequency", reverse = TRUE, nrow = 2))

plot_internet_freq

ggsave("plot_internet_freq.jpg", plot_internet_freq,
       width = 12,
       height = 4)

```

## topics of interest (Q8 on questionnaire)
```{r}
by_topic <- x_2022_september_qualtrics_data %>%
  select(starts_with("which_topics")) %>%
  rename_all(~stringr::str_replace(.,"which_topics_","")) %>%
  mutate_all(funs(replace(., !is.na(.), 1))) %>%
  mutate_all(funs(as.numeric))

# number of topics selected per participant
n_topics_per_participants <- by_topic %>%
  rowwise() %>% 
  mutate(sum = sum(c_across(where(is.numeric)), na.rm = T))

round(mean(n_topics_per_participants$sum), 1)
round(sd(n_topics_per_participants$sum), 2)
range(n_topics_per_participants$sum)

# boxplot showing number of choices
plot_n_topics_interested <- ggplot(n_topics_per_participants, aes(x=factor(0), y=sum))+
  geom_boxplot() +
  scale_y_continuous(breaks = seq(0, 8, by = 1)) +
  geom_jitter(width = 0.25, height = 0.25, alpha = 0.5) +
  #geom_point(aes(y=sum), color="black") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.4, alpha = 0.65)+
  theme_minimal(base_size = 20) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(y = "Number of topics selected")

ggsave("plot_n_topics_interested.jpg", plot_n_topics_interested,
       width = 6,
       height = 8)

# violin plot showing number of choices (with mean being set as the reference point)
plot_n_topics_interested_violin <- n_topics_per_participants %>%
  ggplot(aes(x=factor(0), y=sum)) +
  geom_violin() +
  #geom_boxplot(width=0.3, color = "blue") +  
  geom_jitter(shape=19, position=position_jitter(width=0.25,height=0.25), alpha = 0.5) +
  #geom_jitter(width = 0.25, height = 0.1, alpha = 0.5) +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.35, alpha = 0.25) +
  stat_summary(fun = "mean",
               geom = "crossbar", 
               #width = 0.5,
               colour = "red", 
               ) +
  #stat_summary(fun = "median",
  #             geom = "crossbar",
  #             color = "blue",
  #             linetype = "dashed") +
  scale_y_continuous(breaks = seq(0, 8, by = 1)) +
  theme_minimal(base_size = 20) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(y = "Number of topics selected")

ggsave("plot_n_topics_interested_violin.jpg", plot_n_topics_interested_violin,
       width = 5,
       height = 8)


# frequency of topics
topic_sums <- as.data.frame(colSums(by_topic, na.rm=T)) %>%
  arrange(desc(colSums(by_topic, na.rm = T)))

# plot frequency of topics
plot_topic <- by_topic %>%
  pivot_longer(everything(), names_to = "topic", values_to = "selected") %>%
  na.omit() %>%
  group_by(topic) %>%
  count() %>%
  mutate(topic = recode(topic,
                        bilingualism = "Language learning in bilingual environments",
                        screen_time = "The effect of screen time on language learning",
                        lang_diversity = "Language diversity around the world",
                        sign_language = "Learning sign language",
                        foster_language = "Ways to foster language learning",
                        reading_writing = "Ways to foster reading and writing",
                        langauge_dev_disorders = "Ways to foster language learning in \n children with developmental disorders",
                        mythbuster = "Debunking common language learning myths")) %>%
  ggplot(aes(x = reorder(topic, n), y = n)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  theme_minimal(base_size = 20) +
  coord_flip() +
  labs(x = "Topic",
       y = "Number of counts") 
  
plot_topic

ggsave("plot_topic.jpg", plot_topic,
       width = 12,
       height = 8)


#by_topic <- x_2022_september_qualtrics_data %>%
#  select(c(which_topics_bilingualism, which_topics_screen_time, which_topics_lang_diversity, which_topics_sign_langauge, which_topics_foster_language, which_topics_reading_writing, which_topics_langauge_dev_disorders, which_topics_mythbusters))%>%
#  replace_na(list (which_topics_bilingualism = "0")) %>%
#  replace_na(list (which_topics_screen_time = "0")) %>%
#  replace_na(list (which_topics_lang_diversity = "0")) %>%
#  replace_na(list (which_topics_sign_langauge = "0")) %>%
#  replace_na(list (which_topics_foster_language ="0")) %>%
#  replace_na(list (which_topics_reading_writing = "0")) %>%
#  replace_na(list(which_topics_langauge_dev_disorders ="0")) %>%
#  replace_na(list(which_topics_mythbusters ="0")) %>%
#  mutate(which_topics_bilingualism = case_when( which_topics_bilingualism=="0" ~ 0,
#                                              TRUE ~1)) %>%
#    mutate(which_topics_screen_time = case_when( which_topics_screen_time=="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_lang_diversity = case_when( which_topics_lang_diversity=="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_sign_langauge = case_when( which_topics_sign_langauge =="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_foster_language = case_when(which_topics_foster_language=="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_reading_writing = case_when( which_topics_reading_writing=="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_langauge_dev_disorders= case_when( which_topics_langauge_dev_disorders=="0" ~ 0,
#                                              TRUE ~1)) %>%
#      mutate(which_topics_mythbusters = case_when( which_topics_mythbusters=="0" ~ 0,
#                                              TRUE ~1)) 
```

## Helpfulness (Q6 on questionnaire)
```{r}
count_helpfulness <- x_2022_september_qualtrics_data %>%
  filter(!is.na(how_helpful_evidence_based)) %>%
  group_by(how_helpful_evidence_based) %>%
  count(how_helpful_evidence_based)%>%
  ungroup() %>%
  mutate(n_total = sum(n),
         percentage = (n/n_total)*100) %>%
  arrange(desc(percentage))

count_helpfulness

# mode
find_mode(x_2022_september_qualtrics_data$how_helpful_evidence_based)

# mean
helpfulness <- x_2022_september_qualtrics_data %>%
  mutate(helpfulness_numeric = case_when(
    str_detect(how_helpful_evidence_based, "Not at all") ~ 1,
    str_detect(how_helpful_evidence_based, "Somewhat") ~ 2,
    str_detect(how_helpful_evidence_based, "Very helpful") ~ 3,
    TRUE ~ NA_real_))

mean(helpfulness$helpfulness_numeric, na.rm=T)

# plot (n = 145)
plot_helpfulness <- count_helpfulness %>%
  ## remove NAs
  #filter(!is.na(how_helpful_evidence_based)) %>%
  # rename items
  mutate(how_helpful_evidence_based = case_when(
    str_detect(how_helpful_evidence_based, "Not at all") ~ "Not at all helpful",
    str_detect(how_helpful_evidence_based, "Somewhat") ~ "Somewhat helpful",
    str_detect(how_helpful_evidence_based, "Very helpful") ~ "Very helpful")) %>%
  ggplot() + 
  geom_bar(aes(x = factor(0), y = percentage, 
               fill = factor(how_helpful_evidence_based, 
                             levels = c("Very helpful", "Somewhat helpful", "Not at all helpful"))), 
               position="stack", stat="identity") +
  ylab("Percentage") +
  coord_flip() + 
  scale_fill_manual(values = c("#e31a1c", "#d9d9d9", "#3182bd")) +
  theme_minimal(base_size = 20) +
  theme(legend.position="bottom",
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(title="Helpfulness", reverse = TRUE))

plot_helpfulness 

ggsave("plot_helpfulness.jpg", plot_helpfulness,
       width = 12,
       height = 4)

```



## Important features rating: Which features were top/bottom rated? (Q9 on questionnaire)
### Descriptives
First, we will find out the top-3 and bottom-3 features (* removing "other" from the analysis)
```{r}
data_feature <- x_2022_september_qualtrics_data %>%
  ## select relevant variables
  select(response_id, starts_with("importance_"), -starts_with("importance_other")) %>%
  ## transpose data frame
  pivot_longer(-response_id, names_to = "feature", values_to = "rating") %>%
  mutate(feature = as.factor(feature),
         rating = as.numeric(rating)) %>%
  ## recode feature levels
  mutate(feature = recode(feature,
                          "importance_concrete_advice" = "Concrete advice",
                          "importance_free" = "Free",
                          "importance_easy_to_access" = "Easy to access",
                          "importance_understandable" = "Understandable",
                          "importance_engaging" = "Engaging",
                          "importance_EDI" = "Diverse and inclusive",
                          "importance_social_media" = "Linked to social media",
                          "importance_reliable" = "Reliable",
                          "importance_evidence_based" = "Evidence-based",
                          "importance_unpretentious" = "Unpretentious",
                          "importance_respectful" = "Respectful",
                          "importance_fun" = "Fun",
                          "importance_unbiased" = "Unbiased"))

# calculate mean rating per features 
mean_feature_rating <- data_feature %>%
  filter(!is.na(rating)) %>%
  ## calculate mean rating per feature
  group_by(feature) %>%
  summarize(n = n(),
            mean_rating = mean(rating, na.rm=T)) %>%
  arrange(mean_rating) %>% # sort by ascending order as the smaller value indicates greater importance
  ungroup()

#crank::meanranks(data_feature %>%
#                   pivot_wider(id_cols = response_id, names_from = feature, values_from = rating) %>%
#                   select(-response_id))

#plot_mean_feature_rating <- mean_feature_rating %>%
#  ggplot(aes(x = reorder(feature, -mean_rating), y = mean_rating)) +
#  geom_point(size = 5) + 
#  theme_minimal() +
#  scale_y_continuous(limits = c(1, 14), breaks = seq(1, 14, by = 1)) +
#  labs(x = "Feature",
#       y = "Importance rating averaged across participants") + 
#  coord_flip() +
#  annotate("text", x=1, y=2, label="most important ←", color="red") +
#  annotate("text", x=1, y=13, label="→ least important", color ="red")


## visualize all variables by number of participants voted per feature
#plot_feature_all <- data_feature %>%
#  count(rating, feature) %>% # count combos of rating & feature
#  ggplot(aes(x = rating, y = n, fill = factor(feature, levels = as.vector(mean_feature_rating$feature)))) +
#  geom_col(position = "fill") +
#  theme_minimal() +
#  scale_x_continuous(breaks=seq(1, 14, 1)) +
#  scale_fill_manual(values = c("#a50026", "#e31a1c", "#fb9a99", "#ff7f00", "#fdbf6f", 
#                               "#ffed6f", "#b2df8a", "#33a02c", "#02818a",
#                               "#a6cee3", "#1f78b4", "#cab2d6", "#6a3d9a")) +
#  labs(x = "Rating (with 1 being the most important)",
#       y = "Proportion of participants",
#       fill = "Feature")

#plot_feature_per_feature <- data_feature %>%
#  count(rating, feature) %>%
#  group_by(rating) %>%
#  mutate(rating = as.factor(rating),
         #sum = sum(n),
#         prop = n/161,
#         ) %>%
#  ungroup() %>%
#  #mutate(feature = match(as.vector(mean_feature_rating$feature), feature)) %>%
#  #filter(!is.na(rating)) %>%
#  ggplot(aes(x = fct_rev(factor(feature, levels = as.vector(mean_feature_rating$feature))), 
#             y = prop, 
#             fill = rating)) +
#  geom_bar(position="stack", stat="identity") +
#  theme_minimal() +
#  scale_fill_manual(values = c("#a50026", "#e31a1c", "#fb9a99", "#ff7f00", "#fdbf6f", 
#                               "#ffed6f", "#ffff99", "#b2df8a", "#33a02c", "#02818a",
#                               "#a6cee3", "#1f78b4", "#cab2d6", "#6a3d9a",  "#999999")) +
#  coord_flip() +
#  labs(x = "Feature",
#       y = "Proportion of participants",
#       fill = "Importance rating")

```


### Interrater reliability per feature
Here, we run inter-rater reliability analysis on the top-3 and bottom-3 rated features. Each feature is run separately. 
```{r}
# find the top-3 and bottom-3 features (with top_1 = most important, and bottom_1 = least important)
feature_top_1 <- mean_feature_rating %>%
  filter(mean_rating == min(mean_rating))

feature_top_2 <- mean_feature_rating %>%
  filter(rank(mean_rating, ties.method = "min") == 2)

feature_top_3 <- mean_feature_rating %>%
  filter(rank(mean_rating, ties.method = "min") == 3)

# Bottom-1 feature
feature_bottom_1 <- mean_feature_rating %>%
  filter(mean_rating == max(mean_rating))

feature_bottom_2 <- mean_feature_rating %>%
  filter(rank(-mean_rating, ties.method = "min") == 2)

feature_bottom_3 <- mean_feature_rating %>%
  filter(rank(-mean_rating, ties.method = "min") == 3)

# ---- Plot proportion of participants in the top3 and bottom3 features ----
plot_feature_top3_bottom3 <- data_feature %>%
  filter(!is.na(rating)) %>% # remove NAs
  mutate(rating = if_else(rating > 3 & rating < 12, "others", as.character(rating))) %>%
  count(rating, feature) %>%
#  filter(!is.na(rating)) %>% # remove NAs
  group_by(rating) %>%
  mutate(rating = as.factor(rating),
         #sum = sum(n),
         prop = n/mean_feature_rating$n[1],
         percentage = (n/mean_feature_rating$n[1] * 100)) %>%
  ungroup() %>%
  #mutate(feature = match(as.vector(mean_feature_rating$feature), feature)) %>%
  ggplot(aes(x = fct_rev(factor(feature, levels = as.vector(mean_feature_rating$feature))), 
             y = percentage, 
             fill = factor(rating, levels = c("1", "2", "3", "others", "12", "13", "14")))) +
  geom_bar(position="stack", stat="identity") +
  theme_minimal(base_size = 20) +
  scale_fill_manual(labels = c("1st", "2nd", "3rd", "top 4th to bottom 4th", "3rd last", "2nd last", "last"), 
                    values = c("#a50026", "#e31a1c", "#fb9a99", "#d9d9d9", "#6baed6", "#3182bd", "#08519c")) +
  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  coord_flip() +
  labs(x = "Feature",
       y = "Percentage of participants",
       fill = "Importance rating") 
  
ggsave("plot_feature_top3_bottom3.jpg", plot_feature_top3_bottom3,
       width = 12,
       height = 8)

# ---- kendall (for ordinal data; cannot run on individual items?) ----
## overall 
data_feature_overall <- data_feature %>%
  filter(!is.na(rating)) %>%
  pivot_wider(id_cols = feature, names_from = response_id, values_from = rating)

irr::kendall(data_feature_overall %>% select(-feature), correct = FALSE) # The W estimate of 0.358 indicates a moderate effect

## top 3 features
data_feature_top <- data_feature %>%
  filter(feature == feature_top_1$feature & !is.na(rating) |
         feature == feature_top_2$feature & !is.na(rating) | 
         feature == feature_top_3$feature & !is.na(rating)) %>%
  pivot_wider(id_cols = feature, names_from = response_id, values_from = rating) #%>%
  # turn into binary data (1 = rated in top 3, 0 = not)
  #mutate_if(is.numeric, funs(ifelse(. <= 3, 1, 0)))

irr::kendall(data_feature_top %>% select(-feature), correct = FALSE) # The W estimate of 0.295 indicates a small effect

## bottom 3 features
data_feature_bottom <- data_feature %>%
  filter(feature == feature_bottom_1$feature & !is.na(rating) |
         feature == feature_bottom_2$feature & !is.na(rating) | 
         feature == feature_bottom_3$feature & !is.na(rating)) %>%
  pivot_wider(id_cols = feature, names_from = response_id, values_from = rating)

irr::kendall(data_feature_bottom %>% select(-feature), correct = FALSE) # The W estimate of 0.121 indicates a small effect

# ---- kappam.fleiss (not the best test to use) ----
irr::kappam.fleiss(data_feature_top)
irr::kappam.fleiss(data_feature_bottom)

# Top 1: inter-rater
irr_feature_top_1 <- data_feature %>%
  filter(feature == feature_top_1$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_top_1

# Top 2: inter-rater
irr_feature_top_2 <- data_feature %>%
  filter(feature == feature_top_2$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_top_2

# Top 3: inter-rater
irr_feature_top_3 <- data_feature %>%
  filter(feature == feature_top_3$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_top_3

# Bottom 3: inter-rater
irr_feature_bottom_3 <- data_feature %>%
  filter(feature == feature_bottom_3$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_bottom_3

# Bottom 2: inter-rater
irr_feature_bottom_2 <- data_feature %>%
  filter(feature == feature_bottom_2$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_bottom_2

# Bottom 1: inter-rater
irr_feature_bottom_1 <- data_feature %>%
  filter(feature == feature_bottom_1$feature & !is.na(rating)) %>%
  select(-feature) %>%
  pivot_wider(names_from = response_id, values_from = rating) %>%
  irr::kappam.fleiss(.)

irr_feature_bottom_1
```

### relationship between internet search frequency and important features rating
Do people who search the internet more prefer different features from those who search it less?
```{r}
east <- c("China", "Hong Kong (S.A.R.)", "Japan", "Singapore", "United Arab Emirates")

data_relation <- x_2022_september_qualtrics_data %>%
  ## select relevant variables
  select(response_id, country, how_often_internet, starts_with("importance_"), -starts_with("importance_other")) %>%
  ## remove rows where a participant didn't make any response to the feature rating
  filter(if_any(starts_with("importance_"), ~!is.na(.))) %>%
  ## create binary variables
  mutate(
    ### country: West vs. East
    binary_country = factor(case_when(country %in% east ~ "East",
                                           is.na(country) ~ NA_character_,
                                 TRUE ~ "West"),
                                 levels = c("West", "East")),
    ### feature in top 5 or not
    #### any 1 of the features in the top 5
    #binary_feature = case_when(as.numeric(importance_evidence_based) <= 5 | as.numeric(importance_reliable) <= 5 | as.numeric(importance_concrete_advice) <= 5 ~ 1,
    #### all 3 features in the top 5
    #binary_feature = case_when(as.numeric(importance_evidence_based) <= 5 & as.numeric(importance_reliable) <= 5 & as.numeric(importance_concrete_advice) <= 5 ~ 1,
    #### any of the 2 features in the top 5
    binary_feature = case_when(as.numeric(importance_evidence_based) <= 5 & as.numeric(importance_reliable) <= 5 | 
                               as.numeric(importance_evidence_based) <= 5 & as.numeric(importance_concrete_advice) <= 5 |
                               as.numeric(importance_reliable) <= 5 & as.numeric(importance_concrete_advice) <= 5 ~ 1,
                               TRUE ~ 0)) %>%
  ## as.factor(how_often_internet)
  mutate(how_often_internet = factor(how_often_internet,
                                     levels = c("Never", 
                                                "Rarely \r\nA few times a year", 
                                                "Occasionally \r\nOnce a month",
                                                "Often\r\nEvery other week",
                                                "Frequently\r\nMore than once a week"))) %>%
  ## as binary (how_often_internet)
  mutate(binary_how_often_internet = case_when(
    how_often_internet == "Never" | how_often_internet == "Rarely \r\nA few times a year" | how_often_internet == "Occasionally \r\nOnce a month" ~ "less",
    how_often_internet == "Often\r\nEvery other week" | how_often_internet == "Frequently\r\nMore than once a week" ~ "more",
    TRUE ~ NA_character_),
    binary_how_often_internet = as.factor(binary_how_often_internet)
    )

#relation_model <- data_relation %>%
#  select(-c(country, starts_with("importance_"))) %>%
#  glm(binary_feature ~ binary_how_often_internet * binary_country, 
#      family = binomial, 
#      data = .,
#      contrasts = list(binary_how_often_internet = contr.sum(2)/2,
#                       binary_country = contr.sum(2)/2)
#      )

#relation_model_noInteraction <- data_relation %>%
#  select(-c(country, starts_with("importance_"))) %>%
#  glm(binary_feature ~ binary_how_often_internet + binary_country, 
#      family = binomial, 
#      data = .,
#      contrasts = list(binary_how_often_internet = contr.sum(2)/2,
#                       binary_country = contr.sum(2)/2)
#      )

relation_model_noCountry <- data_relation %>%
  select(-c(country, starts_with("importance_"))) %>%
  glmer(binary_feature ~ binary_how_often_internet + (1|response_id), 
      family = binomial, 
      data = .,
      contrasts = list(binary_how_often_internet = contr.sum(2)/2)
      )

anova(relation_model_noCountry, relation_model, test="Chi")

broom.mixed::tidy(relation_model_noCountry) %>%
  as.data.frame %>%
  rename(SE = `std.error`, 
         z = `statistic`,
         p = `p.value`) %>%
  mutate(p = case_when(
    p < .001 ~ "<.001",
    p < .01 ~ "<.01",
    p < .05 ~ "<.05",
    TRUE ~ as.character(round(p,3)))) %>%
  mutate_if(is.numeric, round, digits = 2)

```


## comics and participation mode and mean (Q10 on questionnaire)
```{r}
count_participation<- x_2022_september_qualtrics_data %>%
  filter(!is.na(participate_in_science)) %>%
  group_by(participate_in_science) %>%
  count(participate_in_science) %>%
  ungroup() %>%
  mutate(n_total = sum(n),
         percentage = (n/n_total)*100) %>%
  arrange(desc(percentage))

count_participation

#mode
find_mode(x_2022_september_qualtrics_data$participate_in_science)

#mean
participation <- x_2022_september_qualtrics_data %>%
  mutate(participate_in_science = case_when(
    str_detect(participate_in_science, "discourages") ~ 1,
    str_detect(participate_in_science, "haven't thought") ~ 2,
    str_detect(participate_in_science, "neither") ~ 3,
    str_detect(participate_in_science, "Yes") ~ 4,
    TRUE ~ NA_real_))

mean(helpfulness$helpfulness_numeric, na.rm=T)


# plot (n = 123)
plot_participation <- count_participation %>%
  # remove NAs
  filter(!is.na(participate_in_science)) %>%
  # rename items
  mutate(participate_in_science = case_when(
    str_detect(participate_in_science, "discourages") ~ "Discourage",
    str_detect(participate_in_science, "haven't thought") ~ "Haven't thought about it",
    str_detect(participate_in_science, "neither") ~ "Neither",
    str_detect(participate_in_science, "Yes") ~ "Motivate")) %>%
  ggplot() + 
  geom_bar(aes(x = factor(0), y = percentage, 
               fill = factor(participate_in_science, 
                             levels = c("Motivate", "Neither", "Haven't thought about it", "Discourage"))), 
               position="stack", stat="identity") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 25)) +
  ylab("Percentage") +
  coord_flip() + 
  scale_fill_manual(values = c("#e31a1c", "#d9d9d9", "#6baed6", "#3182bd")) +
  theme_minimal(base_size = 20) +
  theme(legend.position="bottom",
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(title="Participation", reverse = TRUE))

plot_participation

ggsave("plot_participation.jpg", plot_participation,
       width = 12,
       height = 4)

```


## future comic ideas (Q11 on questionnaire)
```{r}
count_idea <- x_2022_september_qualtrics_data %>%
  mutate(comic_ideas = as.factor(comic_ideas)) %>%
  count(comic_ideas)

count_idea 

idea_topics <-  x_2022_september_qualtrics_data %>%
  filter(comic_ideas == "Yes") %>%
  select(comic_ideas, comic_ideas_text)

```


#------------ PLOTS--------------------
Evidence based information
```{r}
#I have made 3 types of graphs so you can pick whatever suits better the poster
evidence <- x_2022_september_qualtrics_data %>%
  select(how_helpful_evidence_based)

evidence_table<- as.data.frame(table(evidence$how_helpful_evidence_based)) 

evidence_table <- evidence_table %>%
  mutate(percentage = (Freq/144)*100) %>%
  mutate(percentage = round(percentage, digits=0)) %>%
  mutate(helpfulness_level = Var1)



evi_plot <- ggplot(evidence_table, aes(x="", y=percentage, fill=helpfulness_level))+
geom_bar(width = 1, stat = "identity") +
  geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5))+
  labs(y="percentage evidence based helpfulness", x="")+  
  scale_fill_manual(values=c("#a7eb96",
"#c9b2daff",
"#ff9bb4"))+
  theme_bw()

evi_plot

#Run this code only if you want to get the pie chart

evi_pie<- evi_plot + coord_polar("y", start=0) + theme_void()

evi_pie

# Run this code for side by side bars, probably we need to change the scale for y though!
evi_plot_col <- ggplot(evidence_table, aes(x=helpfulness_level, y=percentage, fill=helpfulness_level))+
geom_col() +
  labs(y="percentage evidence based helpfulness", x="")+
  geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5))+
  labs(y="percentage evidence based helpfulness", x="")+  
  scale_fill_manual(values=c("#a7eb96",
"#c9b2daff",
"#ff9bb4"))+
  theme_bw()

evi_plot_col

```
Internet search frequency

```{r}

internet <- x_2022_september_qualtrics_data %>%
  select(how_often_internet)

internet_table<- as.data.frame(table(internet$how_often_internet)) 

internet_table <- internet_table %>%
  mutate(percentage = (Freq/142)*100) %>%
    mutate(percentage = round(percentage, digits=0)) %>%
  mutate(internet_search_frequency = Var1)

internet_plot <- ggplot(internet_table, aes(x="", y=percentage, fill=internet_search_frequency))+
geom_bar(width = 1, stat = "identity") +
  geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5))+
  labs(y="percentage internet search freq", x="")+
  scale_fill_manual(values=c("#a7eb96",
"#c9b2daff",
"#ff9bb4",
"#ffc297",
"#f0aae5ff",
"#fff3b6",
"#a7ffd3ff",
"#a4d5eb"))+
  theme_bw()

internet_plot

#Run this code only if you want to get the pie chart

internet_pie<- internet_plot + coord_polar("y", start=0) + theme_void()

internet_pie


```



Calculate the mean importance of each topic
```{r}
mean_importance <- x_2022_september_qualtrics_data %>%
  select(c("importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other"))%>%
  pivot_longer(cols=c("importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other"),names_to = "characteristic", values_to= "rating")%>%
  group_by(characteristic)%>% 
  mutate(rating = as.numeric(as.character(rating)))

mean_importance <- mean_importance %>%
  mutate(characteristic = case_when(characteristic == "importance_concrete_advice" ~ "Concrete advice",
                                    characteristic == "importance_free" ~ "Free",
                                    characteristic == "importance_easy_to_access" ~ "Easy to access",
                                    characteristic == "importance_understandable" ~ "Understandable",
                                    characteristic == "importance_engaging" ~ "Engaging",
                                    characteristic == "importance_EDI" ~ "Diverse and inclusive",
                                    characteristic == "importance_social_media" ~ "Linked to social media",
                                    characteristic == "importance_reliable" ~ "Reliable",
                                    characteristic == "importance_evidence_based" ~ "Evidence-based",
                                    characteristic == "importance_unpretentious" ~ "Unpretentious",
                                    characteristic == "importance_respectful" ~ "Respectful",
                                    characteristic == "importance_fun" ~ "Fun",
                                    characteristic == "importance_unbiased" ~ "Unbiased",
                                    characteristic == "importance_other" ~ "Other reason not listed"))


plot<- mean_importance %>%
  ungroup()%>%
  group_by(characteristic)%>%
  summarise(mean = mean(rating, na.rm=T))

plot<- plot %>%
  mutate(characteristic = fct_reorder(plot$characteristic, plot$mean, .desc = T))
 
ggplot(plot, aes(y=characteristic, x=mean)) +
  geom_point(size=5)+
  theme_bw() +
  labs(x="Importance Ranking 1-14", y="Feature")+
  xlim(1, 14) + 
  annotate("text", y=1, x=3, label="most important <-", color="red") +
  annotate("text", y=1, x=10, label="least important ->", color ="red")

```



calculate the proportion of topics considered to be most interesting by parents. 
```{r}
by_topic <- x_2022_september_qualtrics_data %>%
  select(which_topics_interest)%>%
  drop_na() %>%
mutate ("language learning in bilingual and multilingual contexts" = case_when(str_detect(which_topics_interest,"Language learning in bilingual and multilingual contexts") ~ "1", TRUE ~ "0")) %>%
 mutate ("the effect of screen time on language learning" = case_when(str_detect(which_topics_interest,"The effects of screen time on language learning") ~ "1", TRUE ~ "0")) %>%
   mutate ("language diversity (differences and similarities of languages across the world)" = case_when(str_detect(which_topics_interest,"Language diversity") ~ "1", TRUE ~ "0")) %>%
    mutate ("learning sign languages" = case_when(str_detect(which_topics_interest,"Learning sign languages") ~ "1", TRUE ~ "0")) %>%
    mutate ("ways to foster language learning" = case_when(str_detect(which_topics_interest,"Ways to foster language learning") ~ "1", TRUE ~ "0")) %>%
    mutate ("ways to develop reading/writing abilities" = case_when(str_detect(which_topics_interest,"Ways to develop reading") ~ "1", TRUE ~ "0")) %>%
     mutate ("ways to foster language learning in children with developmental disorders" = case_when(str_detect(which_topics_interest,"Ways to foster language learning in children with developmental disorders") ~ "1", TRUE ~ "0")) %>%
   mutate ("debunking commonly believed myths" = case_when(str_detect(which_topics_interest,"Debunking commonly believed myths") ~ "1", TRUE ~ "0")) %>%
  pivot_longer(cols = c("debunking commonly believed myths", 
                        "ways to foster language learning in children with developmental disorders",
                        "ways to develop reading/writing abilities",
                        "ways to foster language learning",
                        "learning sign languages",
                        "language diversity (differences and similarities of languages across the world)",
                       "the effect of screen time on language learning",
                       "language learning in bilingual and multilingual contexts"), 
               names_to = "topic", values_to = "n") %>%
  filter(n == "1") %>%
    select(topic) %>%
  group_by(topic) %>%
  tally() %>%
  mutate(percentage = (n/sum(n))*100) %>%
  mutate(percentage = round(percentage, digits=0))

by_topic <- by_topic %>%
   mutate(topic = fct_reorder(topic, percentage, .desc = TRUE))
 

bp<- ggplot(by_topic, aes(x="", y=percentage, fill=topic))+
geom_bar(width = 1, stat = "identity") + 
scale_fill_manual(values =c("#a7eb96",
"#c9b2daff",
"#ff9bb4",
"#ffc297",
"#f0aae5ff",
"#fff3b6",
"#a7ffd3ff",
"#a4d5eb"))+
    geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5))+
  labs(y="percentage votes", x="")+
  theme_bw()

bp
 

#Run this code only if you want to get the pie chart

pie<- bp + coord_polar("y", start=0) + theme_void()

pie
```


Do comics make you want to participate in studies?

```{r}
particip<- x_2022_june_qualtrics_data %>%
  select(participate_in_science) 

particip_table<- as.data.frame(table(particip$participate_in_science)) 

particip_table<- particip_table %>%
  mutate(percentage = (Freq/123)*100)%>%
  mutate (percentage = round(percentage, digits=0))%>%
  mutate("participate_in_science" = Var1)

careg_plot <- ggplot(particip_table, aes(x="", y=percentage, fill=`participate_in_science`))+
geom_bar(width = 1, stat = "identity") + geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5))+
  labs(y="percentage of votes", x="")+
  scale_fill_manual(values=c("#a7eb96",
"#c9b2daff",
"#ff9bb4",
"#ffc297"))+
  theme_bw()

careg_plot

careg_pie<- careg_plot + coord_polar("y", start=0) + theme_void()

careg_pie
```


############### STATISTICS ###############

1.linear regressions

```{r}
#First we will need dummy variables and to make internet use into a binary variable (yes or no).
library(fastDummies)

lm1<- x_2022_june_qualtrics_data %>%
  mutate(internet_usage = case_when(str_detect(how_often_internet, "Frequently") ~1,
                                    str_detect(how_often_internet, "Often")~1,
                                    str_detect(how_often_internet, "Occasionally")~1,
                                    TRUE~0)) %>%
  mutate(continent = case_when(country == "Australia" ~"Oceania",
                               country %in% c("Belarus","Denmark","France","Germany","Ireland","Portugal","Russian Federation","Sweden", "United Kingdom of Great Britain and Northen Ireland") ~ "Europe",
                               country %in% c("Brazil","Canada","Chile","Colombia","Mexico","Panama","Peru","United States of America")~"America",
                               country %in% c("China","Hong Kong (S.A.R.)","Japan","Singapore") ~ "Asia",
                               TRUE~"Not specified")) %>%
dummy_cols(select_columns = "gender", ignore_na = T) %>%
  dummy_cols(select_columns = "continent", ignore_na = T)=
lm1<- clean_names(lm1) %>%
  filter(!is.na(gender)) %>%
  filter(!is.na(continent))

#boxplots to visually demonstrate changes by gender and continent
ggplot(lm1, aes(x=gender, y=internet_usage))+
  geom_boxplot(na.rm=T)

ggplot(lm1, aes(x=continent, y=internet_usage))+
  geom_boxplot(na.rm=T)


#Does not converge when adding multiple genders. Being female does not explain variance
i1<- glm(internet_usage~ gender_female, data=lm1, family="binomial")
i1m <- glm(internet_usage~ gender_male, data=lm1, family="binomial")

#Living in america marginal effect?
i2<- glm(internet_usage ~ continent_america, data=lm1, family = "binomial")
i2e<-  glm(internet_usage ~ continent_europe, data=lm1, family = "binomial")
i2as <- glm(internet_usage ~ continent_asia, data=lm1, family = "binomial")

summary(i1)
summary(i1m)
summary(i2)
summary(i2e)
summary(i2as)


#correlation matrix?

cor<- lm1 %>%
  select(internet_usage, importance_concrete_advice, importance_free, importance_easy_to_access, importance_understandable, importance_engaging, importance_edi, importance_fun, importance_reliable, importance_social_media, importance_evidence_based, importance_unpretentious, importance_other, importance_respectful, importance_unbiased) 

cor<- as.data.frame(lapply(cor, as.numeric))

head(cor)

mat<- cor(cor, method="pearson", use="complete.obs")

res_corr <- as.data.frame(round(mat,2)) #this data frame has a correlation matrix





```
