---
title: "Kotoboo_data_viz"
author: "ASM"
date: "04/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
library(janitor)
library(readxl)
library(stringr)

```


Read in data
```{r}
x_2022_may_qualtrics_data <- read_excel("2022_may_qualtrics_data.xlsx", col_names=c("start_date", "end_date", "status", "progress", "duration_s", "finished", "recorded_date", "response_id","distribution_channel", "user_language", "recaptcha_score","consent", "year_birth", "gender","country", "caregiver_type","visit_kotoboo", "how_helpful_evidence_based", "how_often_internet","which_topics_interest","importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other","importance_other_text", "participate_in_science", "comic_ideas", "comic_ideas_text", "score", "q_language"))

x_2022_may_qualtrics_data<- x_2022_may_qualtrics_data [-c(1,2,3,4),]
```


Exclude data
```{r}
x_2022_may_qualtrics_data<- x_2022_may_qualtrics_data %>%
  filter(year_birth <=2004) %>%
  filter(year_birth >=1922) %>%
  filter(consent=="I consent") ##86 participants after exclusions

#completion range

range(as.numeric(x_2022_may_qualtrics_data$progress)) #31-100 completed
```
##completion rate stats
```{r}
average_pop <- x_2022_may_qualtrics_data %>%
  select(progress)%>%
  filter(progress!="100") 

mean(as.numeric(average_pop$progress))

table(average_pop$progress)

mean(as.numeric(x_2022_may_qualtrics_data$duration_s))
median(as.numeric(x_2022_may_qualtrics_data$duration_s))
table(x_2022_may_qualtrics_data$duration_s)
```


Get demographic info
```{r}


#Age range
x_2022_may_qualtrics_data <- x_2022_may_qualtrics_data %>%
  mutate(survey_year = 2022) %>%
  mutate(age = survey_year - as.numeric(year_birth))

range(x_2022_may_qualtrics_data$age) #19-48
mean(x_2022_may_qualtrics_data$age) #35.37

#Gender
sum(x_2022_may_qualtrics_data$gender=="Female", na.rm = T) #68
sum(x_2022_may_qualtrics_data$gender=="Male", na.rm = T)  # 15
sum(x_2022_may_qualtrics_data$gender=="Prefer not to answer", na.rm = T) #2
#NA = 1


```


3. By country info
```{r}

table(x_2022_may_qualtrics_data$country)

#Map plot or pie chart with country representation
```


4. Caregiver info
```{r}
#A. Percentage of caregivers
careg<- x_2022_may_qualtrics_data %>%
  select(caregiver_type)

careg_table<- as.data.frame(table(careg$caregiver_type)) 

careg_table<- careg_table %>%
  mutate(percentage = (Freq/110)*100)

#How to make the graph more informative?? 

```

5. Kotoboo visits
```{r}
visits<- x_2022_may_qualtrics_data %>%
  select(visit_kotoboo)

visits_table<- as.data.frame(table(visits$visit_kotoboo)) 

visits_table<- visits_table %>%
  mutate(percentage = (Freq/110)*100)
```
Highest visits category = Never 56%. Then sometimes 10%. This means that out of the people who do visit the site they only look for some comics, or only visit sporadically. Pretty normal. 


6. Evidence based information
```{r}
evidence <- x_2022_may_qualtrics_data %>%
  select(how_helpful_evidence_based)

evidence_table<- as.data.frame(table(evidence$how_helpful_evidence_based)) 

evidence_table <- evidence_table %>%
  mutate(percentage = (Freq/110)*100) %>%
  mutate(helpfulness_level = Var1)

evi_plot <- ggplot(evidence_table, aes(x="", y=percentage, fill=helpfulness_level))+
geom_bar(width = 1, stat = "identity") +
  labs(y="percentage evidence based helpfulness", x="")+
  theme_bw()

evi_plot

#Run this code only if you want to get the pie chart

evi_pie<- evi_plot + coord_polar("y", start=0)

evi_pie

```
7. Internet search frequency

```{r}

internet <- x_2022_may_qualtrics_data %>%
  select(how_often_internet)

internet_table<- as.data.frame(table(internet$how_often_internet)) 

internet_table <- internet_table %>%
  mutate(percentage = (Freq/110)*100) %>%
  mutate(internet_search_frequency = Var1)

internet_plot <- ggplot(internet_table, aes(x="", y=percentage, fill=internet_search_frequency))+
geom_bar(width = 1, stat = "identity") +
  labs(y="percentage internet search freq", x="")+
  theme_bw()

internet_plot

#Run this code only if you want to get the pie chart

internet_pie<- internet_plot + coord_polar("y", start=0)

internet_pie
```



8. Calculate the mean importance of each topic
```{r}
mean_importance <- x_2022_may_qualtrics_data %>%
  select(c("importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other"))%>%
  pivot_longer(cols=c("importance_concrete_advice", "importance_free","importance_easy_to_access", "importance_understandable", "importance_engaging","importance_EDI", "importance_social_media", "importance_reliable","importance_evidence_based", "importance_unpretentious", "importance_respectful","importance_fun", "importance_unbiased", "importance_other"),names_to = "characteristic", values_to= "rating")%>%
  group_by(characteristic)%>% 
  mutate(rating = as.numeric(as.character(rating)))

mean_importance <- mean_importance %>%
  mutate(characteristic = case_when(characteristic == "importance_concrete_advice" ~ "gives concrete advice",
                                    characteristic == "importance_free" ~ "the content is free",
                                    characteristic == "importance_easy_to_access" ~ "it's easy to access",
                                    characteristic == "importance_understandable" ~ "content is understandable",
                                    characteristic == "importance_engaging" ~ "content is engaging",
                                    characteristic == "importance_EDI" ~ "fosters equity, diversity and inclusion",
                                    characteristic == "importance_social_media" ~ "shareable in social media",
                                    characteristic == "importance_reliable" ~ "the information is reliable",
                                    characteristic == "importance_evidence_based" ~ "the content is evidence based",
                                    characteristic == "importance_unpretentious" ~ "the content is unpretentious",
                                    characteristic == "importance_respectful" ~ "the content is respectful",
                                    characteristic == "importance_fun" ~ "the content is fun",
                                    characteristic == "importance_unbiased" ~ "the content is unbiased",
                                    characteristic == "importance_other" ~ "other reason not listed"))


plot<- mean_importance %>%
  ungroup()%>%
  group_by(characteristic)%>%
  summarise(mean = mean(rating, na.rm=T))

plot<- plot %>%
  mutate(characteristic = fct_reorder(plot$characteristic, plot$mean, .desc = T))
 
ggplot(plot, aes(y=characteristic, x=mean)) +
  geom_point(size=5)+
  theme_bw() +
  labs(x="Importance Ranking 1-14", y="Feature")+
  xlim(1, 14) + 
  annotate("text", y=1, x=3, label="most important <-", color="red") +
  annotate("text", y=1, x=10, label="least important ->", color ="red")
  


#change the x axis scale to 0-14 and change the variables names 

 
```



9. calculate the proportion of topics considered to be most interesting by parents. 
```{r}
by_topic <- x_2022_may_qualtrics_data %>%
  select(which_topics_interest)%>%
  drop_na() %>%
mutate ("language learning in bilingual and multilingual contexts" = case_when(str_detect(which_topics_interest,"Language learning in bilingual and multilingual contexts") ~ "1", TRUE ~ "0")) %>%
 mutate ("the effect of screen time on language learning" = case_when(str_detect(which_topics_interest,"The effects of screen time on language learning") ~ "1", TRUE ~ "0")) %>%
   mutate ("language diversity (differences and similarities of languages across the world)" = case_when(str_detect(which_topics_interest,"Language diversity") ~ "1", TRUE ~ "0")) %>%
    mutate ("learning sign languages" = case_when(str_detect(which_topics_interest,"Learning sign languages") ~ "1", TRUE ~ "0")) %>%
    mutate ("ways to foster language learning" = case_when(str_detect(which_topics_interest,"Ways to foster language learning") ~ "1", TRUE ~ "0")) %>%
    mutate ("ways to develop reading/writing abilities" = case_when(str_detect(which_topics_interest,"Ways to develop reading") ~ "1", TRUE ~ "0")) %>%
     mutate ("ways to foster language learning in children with developmental disorders" = case_when(str_detect(which_topics_interest,"Ways to foster language learning in children with developmental disorders") ~ "1", TRUE ~ "0")) %>%
   mutate ("debunking commonly believed myths" = case_when(str_detect(which_topics_interest,"Debunking commonly believed myths") ~ "1", TRUE ~ "0")) %>%
  pivot_longer(cols = c("debunking commonly believed myths", 
                        "ways to foster language learning in children with developmental disorders",
                        "ways to develop reading/writing abilities",
                        "ways to foster language learning",
                        "learning sign languages",
                        "language diversity (differences and similarities of languages across the world)",
                       "the effect of screen time on language learning",
                       "language learning in bilingual and multilingual contexts"), 
               names_to = "topic", values_to = "n") %>%
  filter(n == "1") %>%
    select(topic) %>%
  group_by(topic) %>%
  tally() %>%
  mutate(prop = n/sum(n))

by_topic <- by_topic %>%
   mutate(topic = fct_reorder(topic, prop, .desc = TRUE))
 

bp<- ggplot(by_topic, aes(x="", y=prop, fill=topic))+
geom_bar(width = 1, stat = "identity") + 
scale_fill_manual(values =c("#a7eb96",
"#c9b2da",
"#ff9bb4",
"#ffc297",
"#fff3b6",
"#a4d5eb",
"#8c510a",
"#01665e"))+
  labs(y="proportion (topic votes/total votes)", x="")+
  theme_bw()

bp
 

#Run this code only if you want to get the pie chart

pie<- bp + coord_polar("y", start=0)

pie
```


10. Do comics make you want to participate in studies?

```{r}

```


############### STATISTICS ###############

1.lmms

```{r}
#how_often_internet ~ gender + country + (1|subject) ?? As it is I don't think caregivertype is really interesting


```

2. Linear regression

```{r}
#internet search correlated with most important factor. I think we need a boxplot first.

#how_often_internet ~ importance. What is the intercept here?? I'm a bit confused about the predictor because we have them as separate columns per topic. Is each topics importance a predictor? Not sure that will converge. Do we make a model for each topic? Or do we somehow make a summary column about the mean importance and use that as a predictor?


```


```




